---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
  [![R-CMD-check](https://github.com/AdamSadowski/heir/workflows/R-CMD-check/badge.svg)](https://github.com/AdamSadowski/heir/actions)
  <!-- badges: end -->

# heir

Healthy Eating Index (HEI) scoring is not the simplest of calculations. But this package simply does it! Function hei() will compute HEI-2015 total and component scores using data from 'ASA24' (2016 version and subsequent versions). It implements the 'simple HEI scoring algorithm' as described at <https://epi.grants.cancer.gov/hei/hei-methods-and-calculations.html>. The 'ASA24' system is described at <https://epi.grants.cancer.gov/asa24>. HEI-2015 is described by Krebs-Smith et al. (2018) <doi:10.1016/j.jand.2018.05.021>. 

## Installation

You can install the released version of heir from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("heir")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AdamSadowski/heir")
```

## Quick demo

Adding HEI columns to the end of a data frame via `hei()`:

1) Example data:

```{r example}
library(heir)

asa.df <- read.csv("./tests/testthat/asa_example_df.csv")

asa.df
```

2) `hei()` creates HEI variables for each row. It accepts a data frame and returns it with these added variables. 

```{r}
df <- hei(asa.df)

# grep just to show X and HEI variables

df[, grep("X|HEI", names(df))]

```
